Methods for Large Scale Learning to Rank

### 2014-09-18 report/Chapters/Introduction.tex
nieuwe iteratie implementation
2e iteratie resutls

\section{Motivation and Problem Statement}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance for a given query. Ranking has become a vital part of web search, where commercial search engines help users find their need in the extremely large collection of the World Wide Web. One can find useful applications of ranking in many application domains outside web search as well. For example, it plays a vital role in amongst others: automatic document summarisation, machine translation, drug discovery and in determining the ideal order of maintenance operations \cite{Rudin2009}. In addition, the ranking task has been argued to be more fitting to recommender systems than regression-based rating prediction on a continuous scale \cite{Adomavicius2005,McNee2006}.\\

@@

\subsection{Methodology for Research Question II}
To find an answer to the second research question, the Learning-to-Rank methods determined in the first research question will be implemented in the MapReduce framework and training time will be measured as a factor of the number of cluster nodes used to perform the computation. The HDInsight cloud-based MapReduce platform from Microsoft will be used to run the Learning-to-Rank algorithms on. HDInsight is based on the popular open source MapReduce implementation Hadoop\footnote{http://hadoop.apache.org/}.\\

>>>>

\section{Motivation and Problem Statement}
\label{sec:motivation}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance for a given query. Ranking has become a vital part of web search, where commercial search engines help users find their need in the extremely large collection of the World Wide Web. One can find useful applications of ranking in many application domains outside web search as well. For example, it plays a vital role in amongst others: automatic document summarisation, machine translation, drug discovery and in determining the ideal order of maintenance operations \cite{Rudin2009}. In addition, the ranking task has been argued to be more fitting to recommender systems than regression-based rating prediction on a continuous scale \cite{Adomavicius2005,McNee2006}.\\

@@

\subsection{Methodology for Research Question II}
\label{ssec:rq2_methodology}
To find an answer to the second research question, the Learning-to-Rank methods determined in the first research question will be implemented in the MapReduce framework and training time will be measured as a factor of the number of cluster nodes used to perform the computation. The HDInsight cloud-based MapReduce platform from Microsoft will be used to run the Learning-to-Rank algorithms on. HDInsight is based on the popular open source MapReduce implementation Hadoop\footnote{http://hadoop.apache.org/}.\\

### 2014-09-18 report/Chapters/Results.tex
2e iteratie resutls

This chapter describes and discusses the results of the running time measurements of the cluster and baseline implementations as described in \ref{chap:implementation}. In addition, ranking accuracy results are included to validate the correctness of the Learning to Rank algorithm implementations.
\section{ListNet}
\subsection{Ranking accuracy}
\begin{table}[!h]
\centering
\begin{tabular}{p{6cm}p{1.6cm}p{1.4cm}r}\toprule
Dataset & RankLib & Cluster & Official evaluation \\
\midrule
OHSUMED (LETOR 3.0 version)     & 0.29          &   TODO & 0.3793 \\
MQ2008      					& 0.3865        &   TODO & 0.4689 \\
MQ2007      					& 0.2873        &   TODO & 0.4767 \\
MSLR-WEB10K 					& 0.1744     	&   TODO & - \\
MSLR-WEB30K 					& 0.1837     	&   TODO & - \\
\bottomrule
\end{tabular}
\caption{\acs{NDCG}@10 performance on the testing set on the first fold}
\label{tbl:accuracy_comparison}
\end{table}

\subsection{Speedup}
Figure \ref{fig:listnet_train_time} and Figure \ref{fig:listnet_train_time_log} (which presents the same data with a logarithmic data size axis) show the processing times of a single training iteration using the ListNet implementation included in RankLib library and the cluster implementation described in chapter \ref{chap:implementation} with different numbers of data nodes. The horizontal positions of the measurements are identical between execution method, as they are determined by the collection of datasets used. As previously described in the methodology section, the LETOR 3.0, LETOR 4.0 and MSLR-WEB10/30K datasets are used, supplemented with generated datasets that are multiplications of MSLR-WEB30K. Table \ref{tbl:recap_datasets} describes the datasets used in the experiments.\\

>>>>

This chapter describes and discusses the results of the running time measurements of the cluster and baseline implementations as described in \ref{chap:implementation}. In addition, ranking accuracy results are included to validate the correctness of the Learning to Rank algorithm implementations.
\section{ListNet}
\subsection{Ranking accuracy}
\begin{table}[!h]
\centering
\begin{tabular}{p{6cm}p{1.6cm}p{1.4cm}r}\toprule
Dataset & RankLib & Cluster & Official evaluation \\
\midrule
OHSUMED (LETOR 3.0 version)     & 0.29          &   TODO & 0.3793 \\
MQ2008      					& 0.3865        &   TODO & 0.4689 \\
MQ2007      					& 0.2873        &   TODO & 0.4767 \\
MSLR-WEB10K 					& 0.1744     	&   TODO & - \\
MSLR-WEB30K 					& 0.1837     	&   TODO & - \\
\bottomrule
\end{tabular}
\caption{\acs{nDCG}@10 performance on the testing set on the first fold}
\label{tbl:accuracy_comparison}
\end{table}

\subsection{Speedup}
Figure \ref{fig:listnet_train_time} (linear data size axis) and Figure \ref{fig:listnet_train_time_log} (logarithmic data size axis) show the processing times of a single iteration of the ListNet training algorithm, using the ListNet implementation included in the RankLib library as well as the cluster implementation described in chapter \ref{chap:implementation} with different numbers of data nodes. The horizontal positions of the measurements are identical between execution method, as they are originate from the data sizes of the datasets used. Measurements were performed on a set of datasets consisting of the LETOR 3.0 OHSUMED dataset, LETOR 4.0 datasets and the MSLR-WEB10/30K datasets are used, supplemented with generated datasets that are multiplications of MSLR-WEB30K (as described in section \ref{ssec:rq2_methodology}). Table \ref{tbl:recap_datasets} describes the datasets used in the experiments and their single training fold data sizes.\\
